Appendix

### 2020-04-30 appendix/appendixV5.Rmd
Change order plots. Coef labels.

kable(aux) %>%
  kable_styling(position = "center")

@@

f2 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1)) 
f2
```

```{r,include=F,warning=F}
f2 + 
  labs(caption = "PCTGDP x N") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 18, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

@@

@@

```{r,include=F,warning=F}
f4 + 
  labs(caption = "PCTGDP x logN") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 18, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

f5 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1))

f5
```

```{r,include=F,warning=F}
f5 + 
  labs(caption = "logExpPC x logN") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 18, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

@@

```{r,include=F,warning=F}
f6 + 
  labs(caption = "ExpPC x K") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 18, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

@@

```{r,include=F,warning=F}
blank = ggplot() + 
  geom_blank() +
  theme_minimal()
blank
ggsave("./plots/zz_blank.png", width = 30, height = 18.75, units = "cm")

@@

f9 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 10, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1)) 
f9
```

```{r,include=F,warning=F}
f9 + 
  labs(caption = "PCTGDP x N") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 13, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

@@

@@

```{r,include=F,warning=F}
f11 + 
  labs(caption = "PCTGDP x logN") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 20, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

f12 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1))

f12
```

```{r,include=F,warning=F}
f12 + 
  labs(caption = "logExpPC x logN") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

f13 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 12, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1))

@@

```{r,include=F,warning=F}
f13 + 
  labs(caption = "ExpPC x K") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 12, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

@@

mod1 <- tibble(
  estimate = mod[["beta"]],
  se = mod[["se"]],
  tval = mod[["zval"]],
  pval = mod[["pval"]],
  ci.lb = mod[["ci.lb"]],
  ci.ub = mod[["ci.ub"]],
  model = "PCTGDP"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

kable(mod1) %>%
  kable_styling(position = "center")

@@

mod1_permu <- tibble(
  estimate = mod[["beta"]],
  se = mod[["se"]],
  tval = mod[["zval"]],
  pval = mod[["pval"]],
  ci.lb = mod[["ci.lb"]],
  ci.ub = mod[["ci.ub"]],
  model = "PCTGDP - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

kable(mod1_permu) %>%
  kable_styling(position = "center")

@@

mod2 <- tibble(
  estimate = mod[["beta"]],
  se = mod[["se"]],
  tval = mod[["zval"]],
  pval = mod[["pval"]],
  ci.lb = mod[["ci.lb"]],
  ci.ub = mod[["ci.ub"]],
  model = "PCTGDP - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

kable(mod2) %>%
  kable_styling(position = "center")

@@

mod2_permu <- tibble(
  estimate = mod[["beta"]],
  se = mod[["se"]],
  tval = mod[["zval"]],
  pval = mod[["pval"]],
  ci.lb = mod[["ci.lb"]],
  ci.ub = mod[["ci.ub"]],
  model = "PCTGDP - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

kable(mod2_permu) %>%
  kable_styling(position = "center")

@@

mod3 <- tibble(
  estimate = mod[["beta"]],
  se = mod[["se"]],
  tval = mod[["zval"]],
  pval = mod[["pval"]],
  ci.lb = mod[["ci.lb"]],
  ci.ub = mod[["ci.ub"]],
  model = "ExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

kable(mod3) %>%
  kable_styling(position = "center")

@@

mod3_permu <- tibble(
  estimate = mod[["beta"]],
  se = mod[["se"]],
  tval = mod[["zval"]],
  pval = mod[["pval"]],
  ci.lb = mod[["ci.lb"]],
  ci.ub = mod[["ci.ub"]],
  model = "ExpPC - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

kable(mod3_permu) %>%
  kable_styling(position = "center")

@@

mod4 <- tibble(
  estimate = mod[["beta"]],
  se = mod[["se"]],
  tval = mod[["zval"]],
  pval = mod[["pval"]],
  ci.lb = mod[["ci.lb"]],
  ci.ub = mod[["ci.ub"]],
  model = "ExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

kable(mod4) %>%
  kable_styling(position = "center")

@@

mod4_permu <- tibble(
  estimate = mod[["beta"]],
  se = mod[["se"]],
  tval = mod[["zval"]],
  pval = mod[["pval"]],
  ci.lb = mod[["ci.lb"]],
  ci.ub = mod[["ci.ub"]],
  model = "ExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

kable(mod4_permu) %>%
  kable_styling(position = "center")

@@

mod5 <- tibble(
  estimate = mod[["beta"]],
  se = mod[["se"]],
  tval = mod[["zval"]],
  pval = mod[["pval"]],
  ci.lb = mod[["ci.lb"]],
  ci.ub = mod[["ci.ub"]],
  model = "logExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

kable(mod5) %>%
  kable_styling(position = "center")

@@

mod5_permu <- tibble(
  estimate = mod[["beta"]],
  se = mod[["se"]],
  tval = mod[["zval"]],
  pval = mod[["pval"]],
  ci.lb = mod[["ci.lb"]],
  ci.ub = mod[["ci.ub"]],
  model = "logExpPC - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

kable(mod5_permu) %>%
  kable_styling(position = "center")

@@

mod6 <- tibble(
  estimate = mod[["beta"]],
  se = mod[["se"]],
  tval = mod[["zval"]],
  pval = mod[["pval"]],
  ci.lb = mod[["ci.lb"]],
  ci.ub = mod[["ci.ub"]],
  model = "logExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

kable(mod6) %>%
  kable_styling(position = "center")

@@

mod6_permu <- tibble(
  estimate = mod[["beta"]],
  se = mod[["se"]],
  tval = mod[["zval"]],
  pval = mod[["pval"]],
  ci.lb = mod[["ci.lb"]],
  ci.ub = mod[["ci.ub"]],
  model = "logExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))

kable(mod6_permu) %>%
  kable_styling(position = "center")

@@

```{r}
aux = bind_rows(
  mod1,
  mod3,
  mod5
) %>%
  mutate(model = gsub(" .*", "", model))

kable(aux) %>%
  kable_styling(position = "center")

@@

```{r,echo=F}
aux = bind_rows(
  mod1_permu,
  mod3_permu,
  mod5_permu
) %>%
  mutate(model = gsub(" .*", "", model))

kable(aux) %>%
  kable_styling(position = "center")

>>>>

kable(aux, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

f2 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1))

f2
```

```{r,include=F,warning=F}
f2 + 
  labs(caption = "ExpPC x K") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 18, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

@@

```{r,include=F,warning=F}
f4 + 
  labs(caption = "logExpPC x logN") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 18, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

### PCTGDP x N

f5 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1)) 
f5
```

```{r,include=F,warning=F}
f5 + 
  labs(caption = "PCTGDP x N") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 18, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

\newpage
### PCTGDP x logN

@@

@@

```{r,include=F,warning=F}
f6 + 
  labs(caption = "PCTGDP x logN") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 18, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

@@

\newpage
```{r,include=F,warning=F}
blank = ggplot() + 
  geom_blank() +
  theme_minimal()
blank
ggsave("./plots/zz_blank.png", width = 30, height = 18.75, units = "cm")

@@

f9 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 12, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1))

f9
```

```{r,include=F,warning=F}
f9 + 
  labs(caption = "ExpPC x K") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 12, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

@@

```{r,include=F,warning=F}
f11 + 
  labs(caption = "logExpPC x logN") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

f12 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 10, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1)) 
f12
```

```{r,include=F,warning=F}
f12 + 
  labs(caption = "PCTGDP x N") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 13, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

@@

f13 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1))

@@

```{r,include=F,warning=F}
f13 + 
  labs(caption = "PCTGDP x logN") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 20, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

@@

mod1 <- tibble(
     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ", 
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "PCTGDP"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
    mutate(model = gsub(" .*", "", model))

kable(mod1, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

collapse_rows_dt <- expand.grid(
    Country =sprintf('Country with a long name %s',c('A','B')),
    State =sprintf('State %s',c('a','b')),
    City =sprintf('City %s',c('1','2')),
    District =sprintf('District %s',c('1','2'))) %>% 
  arrange(Country, State, City) %>% 
  mutate_all(as.character) %>%
  mutate(C1 =rnorm(n()),
         C2 =rnorm(n()))

@@

mod1_permu <- tibble(
     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
    mutate(model = gsub(" .*", "", model))

kable(mod1_permu, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

mod2 <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
    mutate(model = gsub(" .*", "", model))

kable(mod2, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

mod2_permu <- tibble(
     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
    mutate(model = gsub(" .*", "", model))

kable(mod2_permu, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

mod3 <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian", "Method: Panel",
          "Method: IV", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
    mutate(model = gsub(" .*", "", model))

kable(mod3, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

mod3_permu <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian", "Method: Panel",
          "Method: IV", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
    mutate(model = gsub(" .*", "", model))

kable(mod3_permu, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

mod4 <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian",
             "Method: Panel", "Method: IV" ,"AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
    mutate(model = gsub(" .*", "", model))

kable(mod4, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

mod4_permu <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian",
             "Method: Panel", "Method: IV" ,"AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
    mutate(model = gsub(" .*", "", model))

kable(mod4_permu, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

mod5 <- tibble(
   ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
             "Method: Panel", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "logExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
    mutate(model = gsub(" .*", "", model))

kable(mod5, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

mod5_permu <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
             "Method: Panel", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "logExpPC - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
    mutate(model = gsub(" .*", "", model))

kable(mod5_permu, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

mod6 <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
             "Method: Panel", "Method: RDD", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "logExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
    mutate(model = gsub(" .*", "", model))

kable(mod6, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

mod6_permu <- tibble(
  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
             "Method: Panel", "Method: RDD", "AggLevel: States"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  T = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "logExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
    mutate(model = gsub(" .*", "", model))

kable(mod6_permu, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

```{r, echo=F}
aux = bind_rows(
  mod1,
  mod3,
  mod5
) %>%
  mutate(model = gsub(" .*", "", model))

kable(aux, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")

@@

# Table  3  presents  the  meta-regression  results  for  our  restricted  and  extended  samples.   Eachcolumn represents one of the three measures of public spending we discuss in this paper. To reduce the risk of false positives in our analyses, we use permutation tests to calculate significance levelsfor the meta-regressions (Higgins and Thompson 2004).TABLE 3 AROUND HERE: Meta-regression analysis estimating the effect of moderator variables on public expenditure 
#The first two models show the results for public expenditure per capita.  In both the restrictedand the extended samples, we and that models that use푛as an independent variable tend to detect significantly smaller effects when compared to k. This suggests that an additional member in thelower house has a smaller impact on public spending than a member in the upper house. Moreover,
#the results for the extended sample point out that recent studies and larger effects than older ones,and that changing the electoral rules from majoritarian to non-majoritarian increases the effects oflegislature size on per capita expenditure.The third and fourth columns use the logarithm of expenditure per capita as the dependentvariable.   No covariate  is statistically  significant in our  smaller sample,  but two  moderators arenegatively associated with the outcome in our larger study pool.  They both refer to estimationmethods.  Studies that employ panel/fixed effects or regression discontinuity designs (RDDs) havelower coeficients for log expenditure per capita if we take OLS as the reference category

aux = bind_rows(
  mod1_permu,
  mod3_permu,
  mod5_permu
) %>%
  mutate(model = gsub(" .*", "", model))

kable(aux, booktabs = T) %>%
  kable_styling(c("striped", "bordered"), position = "center")
